AP/PA Tables ITHIM Global

### 2022-10-17 summary_tables_PA_AP.Rmd
Read params from excel sheet

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyverse)
#library(plotly)
#library(htmltools)

@@

all_inputs <- read.csv('all_city_parameter_inputs.csv',stringsAsFactors = F)

#all_inputs$cape_town <- all_inputs$accra
#all_inputs$vizag <- all_inputs$sao_paulo

parameter_names <- all_inputs$parameter
parameter_starts <- which(parameter_names != '')
parameter_stops <- c(parameter_starts[-1] - 1, nrow(all_inputs))
parameter_names <- parameter_names[parameter_names != '']
parameter_list <- list()
compute_mode <- 'constant'
for (i in 1:length(parameter_names)) {
  parameter_list[[parameter_names[i]]] <- list()
  parameter_index <- which(all_inputs$parameter == parameter_names[i])
  if (all_inputs[parameter_index,2] == '') {
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs) == x)
      val <- all_inputs[parameter_index,city_index]
      ifelse(val %in% c('T','F'),val,as.numeric(val))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else if (all_inputs[parameter_index,2] == 'constant') {
    indices <- 0
    if (compute_mode == 'sample') indices <- 1:2
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs) == x)
      val <- all_inputs[parameter_index + indices,city_index]
      ifelse(val == '',0,as.numeric(val))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else{
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs) == x)
      if (any(all_inputs[parameter_starts[i]:parameter_stops[i],
                         city_index] != '')) {
        sublist_indices <- which(all_inputs[parameter_starts[i]:parameter_stops[i],city_index] != '')
        thing <- as.list(as.numeric(c(all_inputs[parameter_starts[i]:parameter_stops[i],city_index])[sublist_indices]))
        names(thing) <- c(all_inputs[parameter_starts[i]:parameter_stops[i],2])[sublist_indices]
        thing
      }
    }
    )
    names(parameter_list[[parameter_names[i]]]) <- cities
  }
}

for (i in 1:length(parameter_list))  assign(names(parameter_list)[i],parameter_list[[i]])
```

@@

sl <- list()
for (x in 1:length(cities))
{
  modes <- names(unlist(io[[cities[x]]]$PM_emission_inventory))
  emissions <- as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  city_emissions <- cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2] <- "emissions"
  select <- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes <- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)] <- "other"
  summary <- city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2] <- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits = 1)
  summary <- as.data.frame(summary)
  summary[nrow(summary) + 1,1] <- "Transport share"
  summary[nrow(summary),2] <- as.character(round(pm_trans_share[[cities[x]]] * 100))
  summary[nrow(summary) + 1,1] <- "PM2.5 Conc"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  io[[cities[x]]]$summary_emission <- summary

@@

  summary2 <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary2 <- cbind(summary2$scenario, round(summary2[,2:5], digits = 1))
  summary2$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits = 2)
  names(summary2)[1] <- "Scenario"

>>>>

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyverse)
library(readxl)
#library(plotly)
#library(htmltools)

@@

input_parameter_file <- "InputParameters_v15.0.xlsx"
# scenario definition
scenario_name <- "GLOBAL"
reference_scenario <- 'Baseline'

compute_mode <- 'constant' # constant parameters from the given parameters

all_inputs <- read_excel(input_parameter_file, sheet = "all_city_parameter_inputs")
all_inputs[is.na(all_inputs)] <- ""
all_inputs <- as.data.frame(all_inputs)

# get input parameters into correct format
parameter_names <- all_inputs$parameter
parameter_starts <- which(parameter_names!='')
parameter_stops <- c(parameter_starts[-1] - 1, nrow(all_inputs)) 
parameter_names <- parameter_names[parameter_names!='']
parameter_list <- list()

for(i in 1:length(parameter_names)){
  parameter_list[[parameter_names[i]]] <- list()
  parameter_index <- which(all_inputs$parameter==parameter_names[i]) 
  if(all_inputs[parameter_index,2]=='')  { 
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      val <- all_inputs[parameter_index,city_index]
      ifelse(val%in%c('T','F'),val,ifelse(is.numeric(val), as.numeric(val), as.character(val)))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else if(all_inputs[parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      indices <- 0
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        city_index <- which(colnames(all_inputs)==x)
        val <- all_inputs[parameter_index+indices,city_index]
        ifelse(val=='',0,as.numeric(val))
      })
    }
    if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        indices <- 1:2
        city_index <- which(colnames(all_inputs)==x)  
        val <- all_inputs[parameter_index+indices,city_index] 
        if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
          indices <-0
          city_index <- which(colnames(all_inputs)==x) 
          val <- all_inputs[parameter_index+indices,city_index]} 
        val <- as.numeric(val)
      })
    }
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else{
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      if(any(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')){
        sublist_indices <- which(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')
        thing <- as.list(as.numeric(c(all_inputs[parameter_starts[i]:parameter_stops[i],city_index])[sublist_indices]))
        names(thing) <- c(all_inputs[parameter_starts[i]:parameter_stops[i],2])[sublist_indices]
        thing
      }
    }
    )
    names(parameter_list[[parameter_names[i]]]) <- cities
  }
}

list2env(parameter_list, environment())

# read in global parameters

all_global_inputs <- read_excel(input_parameter_file, sheet = "all_global_parameter_inputs")
all_global_inputs[is.na(all_global_inputs)] <- ""
all_global_inputs <- as.data.frame(all_global_inputs)

# get input parameters into correct format
global_parameter_names <- all_global_inputs$parameter
global_parameter_starts <- which(global_parameter_names!='')
global_parameter_stops <- c(global_parameter_starts[-1] - 1, nrow(all_global_inputs)) 
global_parameter_names <- global_parameter_names[global_parameter_names!='']
global_parameter_list <- list()

for(i in 1:length(global_parameter_names)){
  global_parameter_list[[global_parameter_names[i]]] <- list()
  global_parameter_index <- which(all_global_inputs$parameter==global_parameter_names[i]) 
  if(all_global_inputs[global_parameter_index,2]=='')  {

    global_parameter_list[[global_parameter_names[i]]] <- all_global_inputs[global_parameter_index,'global']

  }else if(all_global_inputs[global_parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      global_parameter_list[[global_parameter_names[i]]] <- ifelse(all_global_inputs[global_parameter_index,'global']=='',
                                                                   0,as.numeric(all_global_inputs[global_parameter_index,'global']))
    }
    else if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      indices <- 1:2
      val <- all_global_inputs[global_parameter_index+indices,'global'] 
      if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
        val <- all_global_inputs[global_parameter_index,'global']} 
      val <- as.numeric(val)
      global_parameter_list[[global_parameter_names[i]]] <- val
    }
  }
}

list2env(global_parameter_list, environment())

dist_cat <- unlist(strsplit(gsub(" ", "", dist_cat, fixed = TRUE), "\\,"))

outcome_age_min <- as.numeric(unlist(strsplit(gsub(" ", "", outcome_age_min, fixed = TRUE), "\\,")))
outcome_age_max <- as.numeric(unlist(strsplit(gsub(" ", "", outcome_age_max, fixed = TRUE), "\\,")))
outcome_age_groups <- unlist(strsplit(gsub(" ", "", outcome_age_groups, fixed = TRUE), "\\,"))

min_age <- as.numeric(min_age)
max_age <- as.numeric(max_age)

day_to_week_scalar <- as.numeric(day_to_week_scalar)

@@

sl <- list()
for (x in 1:length(cities))
{
  print(cities[x])
  modes <- names(unlist(io[[cities[x]]]$PM_emission_inventory))
  emissions <- as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  city_emissions <- cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2] <- "emissions"
  select <- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes <- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)] <- "other"
  summary <- city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2] <- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits = 1)
  summary <- as.data.frame(summary)
  summary[nrow(summary) + 1,1] <- "Transport share"
  summary[nrow(summary),2] <- as.character(round(pm_trans_share[[cities[x]]] * 100))
  summary[nrow(summary) + 1,1] <- "PM2.5 Conc"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  io[[cities[x]]]$summary_emission <- summary

@@

  summary2 <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary2 <- cbind(summary2$scenario, round(summary2[,2:5], digits = 1))
  summary2$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, 2)
  summary2$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits = 2)
  names(summary2)[1] <- "Scenario"
